Last glacial cycle glacier erosion potential in the Alps

### 2021-02-03 articles/erosion/alps-erosion.tex
Fix a few reference keys in manuscript.

    \ian{Furthermore, glacier erosion likely  governs, at least in part, the height of mountains \citep{Egholm.etal.2009,Thomson.etal.2010} through the ``glacier buzz-saw''.
      In turn, evidence suggests that increase erosion rates coincided with global cooling and  Pliestocene glaciations from roughly 2.6\unit{Ma} Bp \citep{Herman.Champagnac.2016}.
      Yet, other work suggests that global weathering rates remained constant over this time period \citep{Willenbring.vonBlanckenburg2010}.
      Examination of contemporary erosion rates across different climates suggest that increased temperatures in glaciated regions lead to higher erosion rates and that erosion rates may have increased towards present \citep{Koppes.Montgomery2009,Koppes.etal.2015,Fernandez.etal.2016}.
      However, understanding the link between climate and glacier erosion in the sedimentary record remains difficult due to time scale biases \citep{Ganti.etal.2016} and the non-linear relationship  between temperature and erosion \citep[e.g.][]{Anderson.etal.2012,Mariotti.etal.2021}}

@@

    But importantly, these hydrological processes are not included in our
    model, so that deglaciation surface meltwater is assumed to instantly exit
    the glacier with no effect on glacier dynamics \ian{ \citep[e.g][]{Werder.etal.2013}
      or glacier erosion  \citep[][]{Iverson.etal.2012,Ugelvig.etal.2018}}.
    The enhanced glacier
    velocity during periods of ice retreat is here modelled to result from
    changes of air temperature alone, propagating through diffusion and
    advection into the ice, increasing the glacier's internal energy through
    temperature and englacial water content, thereby facilitating shear strain
    and eventually activating basal sliding \citep[cf.][]{Aschwanden.etal.2012,
    Seguinot.etal.2016}. Observed feedbacks between surface meltwater and basal
    sliding, not included in the model, presumably further accelerated erosion
    during deglaciation \citep{Herman.etal.2011}. \ian{Furthermore, we omit the
      fluvial transport of sediment, which could well increase sediment discharge
      and erosion with increased melt, so long as additional sediment remains
      available \citep{Delaney.Adhikari.2020}. Rapid glacier erosion can be expected
    to accompany the  ongoing 21st-century deglaciation phase. This process might be
    especially strong on the ice sheets of Greenland and Antarctica where
    polythermal and cold-based glaciers are warming and sliding is increasing
    \citep[e.g.][]{Moon.etal.2012,Overeem.etal.2017}.}

>>>>

    \ian{Furthermore, glacier erosion likely  governs, at least in part, the height of mountains \citep{Egholm.etal.2009,Thomson.etal.2010} through the ``glacier buzz-saw''.
      In turn, evidence suggests that increase erosion rates coincided with global cooling and  Pliestocene glaciations from roughly 2.6\unit{Ma} Bp \citep{Herman.Champagnac.2016}.
      Yet, other work suggests that global weathering rates remained constant over this time period \citep{Willenbring.Von-Blanckenburg.2010}.
      Examination of contemporary erosion rates across different climates suggest that increased temperatures in glaciated regions lead to higher erosion rates and that erosion rates may have increased towards present \citep{Koppes.Montgomery.2009,Koppes.etal.2015,Fernandez.etal.2016}.
      However, understanding the link between climate and glacier erosion in the sedimentary record remains difficult due to time scale biases \citep{Ganti.etal.2016} and the non-linear relationship  between temperature and erosion \citep[e.g.][]{Anderson.etal.2012,Mariotti.etal.2021}}

@@

    But importantly, these hydrological processes are not included in our
    model, so that deglaciation surface meltwater is assumed to instantly exit
    the glacier with no effect on glacier dynamics \ian{ \citep[e.g][]{Werder.etal.2013}
      or glacier erosion  \citep[][]{Iverson.2012,Ugelvig.etal.2018}}.
    The enhanced glacier
    velocity during periods of ice retreat is here modelled to result from
    changes of air temperature alone, propagating through diffusion and
    advection into the ice, increasing the glacier's internal energy through
    temperature and englacial water content, thereby facilitating shear strain
    and eventually activating basal sliding \citep[cf.][]{Aschwanden.etal.2012,
    Seguinot.etal.2016}. Observed feedbacks between surface meltwater and basal
    sliding, not included in the model, presumably further accelerated erosion
    during deglaciation \citep{Herman.etal.2011}. \ian{Furthermore, we omit the
      fluvial transport of sediment, which could well increase sediment discharge
      and erosion with increased melt, so long as additional sediment remains
      available \citep{Delaney.Adhikari.2020}. Rapid glacier erosion can be expected
    to accompany the  ongoing 21st-century deglaciation phase. This process might be
    especially strong on the ice sheets of Greenland and Antarctica where
    polythermal and cold-based glaciers are warming and sliding is increasing
    \citep[e.g.][]{Moon.etal.2012,Overeem.etal.2017}.}
